\bf Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-02-10 main.Rmd
cricketdata change -  with lag dot

<!-- fetching raw data since dot and fielding information not available in dismissal type not available in cricket data gravitas -->

@@

cricket_data<- cricket_tsibble %>% 
  mutate(field = if_else(fielding_wckts==0, "no wickets", ">0 wickets"),
         dot = if_else(dot_balls==0,"no dot balls", ">0 dot balls")) 
```

@@

  #filter(fielding_wckts %in% c(0,1)) %>% 
  cricket_data %>% prob_plot("over","field",
                               hierarchy_model,
                               response = "diff_run_rate",
                               plot_type = "violin",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9),
           overlay = TRUE)  + ggtitle("") + geom_boxplot(width = 0.5)
```

@@

A dot ball is a delivery bowled without any runs scored off it. The number of dot balls is reflective of the quality of bowling in the game. Run rate of an over should ideally decrease if the number of dot balls increase. However, what is the effect of dot balls on runs scored in the subsequent over. Will players  batsman likely to go for big shots because they couldn't score good runs in the previous over? Or they should play consistently and avoid scoring high? Figure \ref{fig:exdot} shows the quantile plot of runs across overs for at least one dot ball per over (facet 1) or no dot balls per over (facet 2).
With at least one dot balls per over, the distribution of difference in run rates as observed through the quantiles plotted have shifted downwards. This implies that run rates are likely to decrease in the subsequent over as a result of dot balls in the previous over.

@@

```{r exdot, fig.cap="10th, 20th, 30th, 40th and 50th quantiles of runs per over are drawn  across overs of the innings with no (facet 1), more than zero (facet 2) dot balls per over. For all quantiles, difference in runs between subsequent overs decrease with at least one dot ball in the previous over.", fig.pos="ht"}

@@

cricket_data %>% 
  #filter(dot_balls %in% c(0, 1, 2)) %>%
  prob_plot("dot",
            "over",
            hierarchy_model,
            response = "diff_run_rate",
            plot_type = "quantile",
            quantile_prob = c(0.1, 0.2, 0.3, 0.4, 0.5),
            symmetric = FALSE)  + ggtitle("")
```

>>>>

<!-- fetching raw data since dot and fielding information not available in dismissal type not available in cricket data gravitas. Also `cricket` is aggregated across overs -->

@@

cricket_data<- cricket_tsibble %>% 
  mutate(field = if_else(fielding_wckts==0, "no wickets", ">0 wickets"),
         dot = if_else(dot_balls==0,"no dot balls", ">0 dot balls"),
         lag_field =  lag(field),
         lag_dot = lag(dot)) %>% filter(lag_field!=0, lag_dot!=0)
```

@@

  #filter(fielding_wckts %in% c(0,1)) %>% 
  cricket_data %>% prob_plot("over","lag_field",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "violin",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9),
           overlay = TRUE)  + ggtitle("") + geom_boxplot(width = 0.5)
```

@@

A dot ball is a delivery bowled without any runs scored off it. The number of dot balls is reflective of the quality of bowling in the game. Run rate of an over should ideally decrease if the number of dot balls increase. However, what is the effect of dot balls on runs scored in the subsequent over. Will players  batsman likely to go for big shots because they couldn't score good runs in the previous over? Or they should play consistently and avoid scoring high? Figure \ref{fig:exdot} shows the quantile plot of runs across overs for at least one dot ball per over (facet 1) or no dot balls per over (facet 2).
With at least one dot balls per over, the distribution of run rates in facet 1 increase slower compared to that in facet 2. This implies that run rates are likely to decrease in the subsequent over as a result of dot balls in the previous over.

@@

```{r exdot, fig.cap="25th, 50th, 75th quantiles of runs per over are drawn  across overs of the innings with no (facet 2), more than zero (facet 1) dot balls per over. For all quantiles, run rates mostly increase at a higher rate in facet 2 compared to facet 1 implying run rates decrease with at least one dot ball in the previous over.", fig.pos="ht"}

@@

cricket_data %>% 
  #filter(dot_balls %in% c(0, 1, 2)) %>%
  prob_plot("lag_dot",
            "over",
            hierarchy_model,
            response = "run_rate",
            plot_type = "quantile",
            quantile_prob = c(0.25, 0.5, 0.75),
            symmetric = FALSE)  + ggtitle("")
```

### 2020-02-10 main.tex
cricketdata change -  with lag dot

\begin{verbatim}
#> # A tibble: 20 x 3
#>    over  `>0 wickets` `no wickets`
#>    <fct>        <dbl>        <dbl>
#>  1 1              125         1039
#>  2 2              155          997
#>  3 3              179          972
#>  4 4              173          978
#>  5 5              189          962
#>  6 6              191          957
#>  7 7              144         1002
#>  8 8              134         1012
#>  9 9              148          993
#> 10 10             157          984
#> 11 11             173          962
#> 12 12             177          951
#> 13 13             169          954
#> 14 14             205          913
#> 15 15             208          892
#> 16 16             219          865
#> 17 17             231          833
#> 18 18             291          743
#> 19 19             287          695
#> 20 20             306          572
\end{verbatim}

@@

\begin{verbatim}
#> # A tibble: 20 x 3
#>    over  `>0 dot balls` `no dot balls`
#>    <fct>          <dbl>          <dbl>
#>  1 1               1146             18
#>  2 2               1140             12
#>  3 3               1111             40
#>  4 4               1112             39
#>  5 5               1099             52
#>  6 6               1099             49
#>  7 7               1057             89
#>  8 8               1026            120
#>  9 9               1027            114
#> 10 10              1010            131
#> 11 11               992            143
#> 12 12               971            157
#> 13 13               970            153
#> 14 14               957            161
#> 15 15               935            165
#> 16 16               904            180
#> 17 17               881            183
#> 18 18               852            182
#> 19 19               788            194
#> 20 20               683            195
\end{verbatim}

@@

\caption{10th, 20th, 30th, 40th and 50th quantiles of runs per over are drawn  across overs of the innings with no (facet 1), more than zero (facet 2) dot balls per over. For all quantiles, difference in runs between subsequent overs decrease with at least one dot ball in the previous over.}\label{fig:exdot}
\end{figure}

>>>>

\begin{verbatim}
#> # A tibble: 20 x 3
#>    over  `>0 wickets` `no wickets`
#>    <fct>        <dbl>        <dbl>
#>  1 1              125         1038
#>  2 2              155          997
#>  3 3              179          972
#>  4 4              173          978
#>  5 5              189          962
#>  6 6              191          957
#>  7 7              144         1002
#>  8 8              134         1012
#>  9 9              148          993
#> 10 10             157          984
#> 11 11             173          962
#> 12 12             177          951
#> 13 13             169          954
#> 14 14             205          913
#> 15 15             208          892
#> 16 16             219          865
#> 17 17             231          833
#> 18 18             291          743
#> 19 19             287          695
#> 20 20             306          572
\end{verbatim}

@@

\begin{verbatim}
#> # A tibble: 20 x 3
#>    over  `>0 dot balls` `no dot balls`
#>    <fct>          <dbl>          <dbl>
#>  1 1               1145             18
#>  2 2               1140             12
#>  3 3               1111             40
#>  4 4               1112             39
#>  5 5               1099             52
#>  6 6               1099             49
#>  7 7               1057             89
#>  8 8               1026            120
#>  9 9               1027            114
#> 10 10              1010            131
#> 11 11               992            143
#> 12 12               971            157
#> 13 13               970            153
#> 14 14               957            161
#> 15 15               935            165
#> 16 16               904            180
#> 17 17               881            183
#> 18 18               852            182
#> 19 19               788            194
#> 20 20               683            195
\end{verbatim}

@@

\caption{25th, 50th, 75th quantiles of runs per over are drawn  across overs of the innings with no (facet 2), more than zero (facet 1) dot balls per over. For all quantiles, run rates mostly increase at a higher rate in facet 2 compared to facet 1 implying run rates decrease with at least one dot ball in the previous over.}\label{fig:exdot}
\end{figure}
